---
title: "Cruz_MA712_HW6_US_SHOOTINGS"
output: html_notebook
---

```{r}
library(tidyverse)
library(Zelig)
library(texreg)
library(mvtnorm)
library(radiant.data)
library(sjmisc)
library(lattice)
library(dplyr)
```
#DATA On US MASS SHOOTINGS
```{r}
library(radiant.data)
library(readr)
  usguns <- read_csv("/Users/racruz/Desktop/US_Mass_Shooting_Dataset.csv", col_names = TRUE)
 head(usguns)
```

#Cleaning Data
```{r}
usguns1<-na.omit(usguns)
head(usguns1)
```
#Changing my DV into integer Var
```{r}
usguns1 <- usguns1%>% 
  mutate(mental_hi = as.factor(Mental_Health_Issues),
         Gender = as.factor(Gender),
         Race = as.factor(Race))
```
#Using the Mental Health Issues Var in the orginal data I made a new variable (mental_hi) which takes the 1 if there was a mental health issue and 0 if there was no mental health issue
```{r}
usguns1 <- usguns1%>%
  mutate(mental_hi= ifelse(Mental_Health_Issues =="Yes",1,0))

head(usguns1)
```
#Filtering my dataset (usguns1)
```{r}
usguns1 %>% 
  select(mental_hi, Fatalities, Injured, Victimtot, Gender, everything())
head(usguns1)
```
#Regression Analysis
The 
```{r}
nm0 <- lm(Fatalities ~ mental_hi + Gender + Race, family = binomial, data = usguns1)
summary(nm0)
visreg::visreg(nm0)
```

```{r}
nm1 <- lm(Fatalities ~ mental_hi + Gender + Race, family = binomial, data = usguns1)
summary(nm1)
```
#Regression Results
The interpretation of this output suggests that there is a statistically significant relationship between number of fatalities and number of those who are injured.  Mental health issues contributes to (0.23) increase in fatalities and a (.011) increase in injuries when mental health is observed.
```{r}
nm2 <- lm(Fatalities ~ mental_hi*Injured + Gender + I(Fatalities^2), family = binomial, data = usguns1)
summary(nm2)
```

#AIC X BIC
Screen Used to simply interpret the data in R.

As seen Model 2 best fits this data. We see that Model 2 has the lowest deviance levels with AIC and BIC lowest at Model 2.
```{r}
library(texreg)
screenreg(list(nm0, nm1,nm2))
```




```{r}
htmlreg(list(nm0, nm1, nm2))
```


#Factor Function
Identifying if the IV's in this analysis are in fact factors

```{r}
(l <- sapply(usguns1, function(x) is.factor(x)))
```




#Zelig EV, PV , FD Interpretations



```{r}
zus.shoot <- zelig(Fatalities ~ mental_hi + Gender + Race, model = "normal", data = usguns1)
zus.shoot
```

```{r}
zus.set <- setx(zus.shoot, Fatalities = min(usguns1$Fatalities):max(usguns1$Fatalities))
zus.sim <- sim(zus.shoot, zus.set)
ci.plot(zus.sim)
```

```{r}
zus.shoot1 <- zelig(Fatalities ~ mental_hi*Race + Gender, model = "normal", data = usguns1)
summary(zus.shoot)
```



```{r}
ftal.range = min(usguns1$Fatalities):max(usguns1$Fatalities)
x <- setx(zus.shoot, Fatalities = ftal.range)
s <- sim(zus.shoot, x = x)
ci.plot(s)
```





```{r}
x <- setx(zus.shoot, Gender = "Male")
x1 <- setx(zus.shoot, Gender = "Female")
s <- sim(zus.shoot, x = x, x1 = x1)
summary(s)
```


```{r}
fd <- s$get_qi(xvalue="x1", qi="fd")
summary(fd)
```

```{r}
graphics.off()
 par("mar")
 par(mar=c(1,1,1,1))
 plot(s)
```



```{r}
c1x <- setx(zus.shoot, Gender = "Male", Fatalities)
c1x1 <- setx(zus.shoot, Gender = "Female", Fatalities)
c1s <- sim(zus.shoot, x = c1x, x1 = c1x1)


graphics.off()
 par("mar")
 par(mar=c(1,1,1,1))
plot(c1s)
```


```{r}
c2x <- setx(zus.shoot, mental_hi*Fatalities, Gender)
c2s <- sim(zus.shoot, x = c2x)

graphics.off()
 par("mar")
 par(mar=c(1,1,1,1))
plot(c2s)
```

```{r}
d1 <- c1s$get_qi(xvalue="x1", qi="fd")
```

```{r}
dfd <- as.data.frame(cbind(d1))
head(dfd)
```

```{r}
library(tidyr)

tidd <- dfd %>% 
  gather(Gender, simv, 1:1)
head(tidd)
```

```{r}
library(dplyr)

tidd %>% 
  group_by(Gender) %>% 
  summarise(mode = mode(simv), sd = sd(simv))
```
```{r}
library(ggplot2)

ggplot(tidd, aes(simv)) + geom_histogram() + facet_grid(~Gender) 
```




